Cross Validation Approaches for Penalized Cox Regression

### 2019-04-03 main.tex
edit 3.3

%The left panel compares the $\lambda$ selected by different methods. Verweij and Van Houwelingen's cross-validated partial likelihood approach, which is currently most widely used approach, consistently selects $\lambda$s that are greater than the optimal one.  Greater $\lambda$ leads to greater penalties and fewer non-zero variables, hence Verweij and Van Houwelingen's approach is conservative in terms of selecting variables. While the proposed cross-validated Deviance residual has very close performance as Verweij and Van Houwelingen's approach, the standard cross-validated log likelihood and the cross-validated linear predictor were more liberal than the other two methods. In general, all four methods tends to act conservatively and selects smaller models.

@@

\bnote{Simulation Updated, still need to work on writing}
As discussed earlier, standard cross-validation cannot be used to carry out leave-one-out cross validation (LOOCV) for Cox regression models.  The three other approaches (V\&VH, linear predictor, and deviance residual), however, are not subject to the stability issues described in Section~\ref{Sec:stability}, and can be used to implement LOOCV.  Here, we compare these three approaches for carrying out LOOCV, and also compare LOOCV to 10-fold CV.

For this study, we conducted both 10-fold CV and LOOCV for the V\&VH, linear predictor, and deviance residual approach, with standard 10-fold cross-validation used as a baseline for comparison.  These results are shown in Figure~\ref{Fig:loocv}. \note{FYI, never write \texttt{Figure 4}; always use \texttt{\textbackslash ref}} For all three methods, LOOCV selected models with a smaller MSE than 10-fold CV. For the V\&VH and deviance residual approaches, however, LOOCV was still was inferior to standard 10-fold CV.  As described in Section~\ref{Sec:stability}, these approaches tend to be conservative, selecting a larger-than-optimal value of the regularization parameter; LOOCV helps with this problem, but does not alleviate it entirely.

For the linear predictor approach, on the other hand, \ldots \note{we need to talk about the linear predictor approach too!}

\begin{figure}[h]
  \centering
  \includegraphics[height= 8cm ]{./manuscript_figure/figure_4.png}
  \caption{\label{Fig:loocv}LOOCV\note{Needs a better caption; also, should y-axis be log mse ratio?}}
\end{figure}

>>>>

@@

\bnote{I edited this section and the figure caption}

As discussed earlier, standard cross-validation cannot be used to carry out leave-one-out cross validation (LOOCV) for Cox regression models. The three other approaches (V\&VH, linear predictor, and deviance residual), however, are not subject to the stability issues described in Section~\ref{Sec:stability}, and can be used to implement LOOCV.  Here, we compare these three approaches for carrying out LOOCV, and also compare LOOCV to 10-fold CV.

\begin{figure}[h]
  \centering
  \includegraphics[height= 8cm ]{./manuscript_figure/figure_4.png}
  \caption{\label{Fig:loocv}Simulation comparing LOO and 10-fold CV across three different approaches. With $N = 200$ replications, the data sets generated have dimension $n = 120$ and $p = 1000$. The horizontal axis is the signal strength. The verticle axis is the $\log$(MSE ratio). In each panel, the LOO version and 10-fold version of the same approach are plotted. The 10-fold standard approach is plotted as the blue line in all three panels as a baseline for comparison. }
\end{figure}

For this simulation experiment, we generated datasets with $n = 120$ and $p = 1000$, using the same data generating procedure as describted in Section~\ref{Sec:accuracy}. For each of the V\&VH, linear predictor, and deviance residual approaches, we conducted both 10-fold CV and LOOCV. We also conducted the standard 10-fold cross-validation as a baseline for comparison. We recorded the model that minimizes the cross-validated error  for each approach. After $N = 200$ replications, $\log$ of the MSE ratio was computed using the same definition described in Section~\ref{Sec:accuracy}.

Results of the simulation are shown in Figure~\ref{Fig:loocv}. The panels illustrate the results for each CV approach, one with the 10-fold version and one with the leave-one-out version. The 10-fold standard approach was plotted in all three panels as a baseline for comparison.  For all three approaches, the Leave-One-Out version selected models with a smaller $\log(\text{MSE ratio})$ than the 10-fold version. For the V\&VH and deviance residual approaches, however, LOOCV was still inferior to standard 10-fold CV.  As described in Section~\ref{Sec:accuracy}, these approaches tend to be conservative, selecting a larger-than-optimal value of the regularization parameter; LOOCV helps with this problem, but does not alleviate it entirely.

For the linear predictor approach, on the other hand, the LOOCV version surpasses the standard 10-fold CV by having smaller $\log(\text{MSE ratio})$ across all signal strength levels. At the same time, even the 10-fold version of the linear predictor approach also outperforms the leave-one-out version of the V$\&$VH approach and the deviance residual approach. That is to say, even though the leave-one-cross validation improves the predictive accuracy for V$\&$VH and deviance residual approach with a higher computation cost, the magnitude of improvement in predictive performance is smaller than switching to the linear predictor approach.
